---
title: "HW8"
author: "A Case Study: Philadelphia Shooting Victims"
date: "Q Liang"
output:
  html_document: 
    toc: yes
    toc_depth: 4
    toc_float: yes
    code_folding: hide
    code_download: yes
    smooth_scroll: yes
    number_sections: yes
    theme: readable
---
<style type="text/css">

div#TOC li {
    list-style:none;
    background-image:none;
    background-repeat:none;
    background-position:0;
}
h1.title {
  font-size: 24px;
  color: DarkRed;
  text-align: center;
}
h4.author { /* Header 4 - and the author and data headers use this too  */
    font-size: 18px;
  font-family: "Times New Roman", Times, serif;
  color: DarkRed;
  text-align: center;
}
h4.date { /* Header 4 - and the author and data headers use this too  */
  font-size: 18px;
  font-family: "Times New Roman", Times, serif;
  color: DarkBlue;
  text-align: center;
}
h1 { /* Header 3 - and the author and data headers use this too  */
    font-size: 22px;
    font-family: "Times New Roman", Times, serif;
    color: darkred;
    text-align: center;
}
h2 { /* Header 3 - and the author and data headers use this too  */
    font-size: 18px;
    font-family: "Times New Roman", Times, serif;
    color: navy;
    text-align: left;
}

h3 { /* Header 3 - and the author and data headers use this too  */
    font-size: 15px;
    font-family: "Times New Roman", Times, serif;
    color: navy;
    text-align: left;
}

h4 { /* Header 4 - and the author and data headers use this too  */
    font-size: 18px;
    font-family: "Times New Roman", Times, serif;
    color: darkred;
    text-align: left;
}
</style>

```{r setup, include=FALSE}
# code chunk specifies whether the R code, warnings, and output 
# will be included in the output files.
options(repos = c(CRAN = "https://cloud.r-project.org"))
if (!require("tidyverse")) {
   install.packages("tidyverse")
   library(tidyverse)
}
if (!require("knitr")) {
   install.packages("knitr")
   library(knitr)
}
if (!require("plotly")) {
   install.packages("plotly")
   library(plotly)
}
if (!require("gapminder")) {
   install.packages("gapminder")
   library(gapminder)
}
#if (!require("RCurl")) {
#    install.packages("RCurl")             # Install RCurl package
#    library("RCurl")
#}
if (!require("colourpicker")) {
    install.packages("colourpicker")              
    library("colourpicker")
}
if (!require("gganimate")) {
    install.packages("gganimate")              
    library("gganimate")
}
if (!require("gifski")) {
    install.packages("gifski")              
    library("gifski")
}
if (!require("magick")) {
    install.packages("magick")              
    library("magick")
}
if (!require("grDevices")) {
    install.packages("grDevices")              
    library("grDevices")
}
if (!require("leaflet")) {
    install.packages("leaflet")              
    library("leaflet")
}
if (!require("maps")) {
    install.packages("maps")              
    library("maps")
}
if (!require("htmltools")) {
    install.packages("htmltools")              
    library("htmltools")
}
if (!require("htmlwidgets")) {
    install.packages("htmlwidgets")              
    library("htmlwidgets")
}
if (!require("leaflegend")) {
    install.packages("leaflegend")              
    library("leaflegend")
}
if (!require("geojsonio")) {
    install.packages("geojsonio")              
    library("geojsonio")
}
if (!require("stringi")) {
    install.packages("stringi")              
    library("stringi")
}
if (!require("RColorBrewer")) {
    install.packages("RColorBrewer")              
    library("RColorBrewer")
}
if (!require("tigris")) {
    install.packages("tigris")              
    library("tigris")
}
if (!require("leafpop")) {
    install.packages("leafpop")              
    library("leafpop")
}
#if (!require("leafem")) {
#    install.packages("leafem")              
#    library("leafem")
#}
#if (!require("tmap")) {
#    install.packages("tmap")              
#    library("tmap")
#}
#if (!require("tmaptools")) {
#    install.packages("tmaptools")              
#    library("tmaptools")
#}
if (!require("webshot2")) {
    install.packages("webshot2")              
    library("webshot2")
}
if (!require("sf")) {
    install.packages("sf",)              
    library("sf")
}
#if (!require("terra")) {
#    install.packages("terra")              
#   library("terra")
#}
if (!require("leafpop")) {
    install.packages("leafpop")              
    library("leafpop")
}
if (!require("lubridate")) {
    install.packages("lubridate")              
    library("lubridate")
}
##
knitr::opts_chunk$set(echo = TRUE,       
                      warning = FALSE,   
                      result = TRUE,   
                      message = FALSE,
                      comment = NA)
```


<BR>
This data set is about the shooting victims at Philadelphia. It collects the data from 2015 and updates continuously. 
<BR>

```{r fig.align='center', fig.height=6, fig.width=8, warning=FALSE, message = FALSE}
#library(sf)
#data0=PhillyShootings
data0  <- na.omit(st_read("https://pengdsci.github.io/STA553VIZ/w08/PhillyShootings.geojson"))
#head(data0)  
#range(data0$year)
##  covid_vaccines_by_census_tract.geojson
phillyNeighbor  <- st_read("https://pengdsci.github.io/STA553VIZ/w08/Neighborhoods_Philadelphia.geojson")
# block level data
philly  <- st_read("https://pengdsci.github.io/STA553VIZ/w08/PhillyNeighborhood-blocks.geojson") 

#map
label.msg <- paste(paste("Year: ",data0$year),
                    paste("Fatal: ",data0$fatal))
fatalColor <- rep("red",dim(data0)[1])
fatalColor[which(data0$fatal==0)] <- "grey"
media = st_as_sf(data.frame(x = -75.2877, y = 40.1),
                 coords = c("x", "y"),
                 crs = 4326)
trend = "https://github.com/liangqs99/HW8/blob/main/annualNumber.png"
leaflet(data0) %>% 
  #addTiles() %>%
  setView(lng=-75.1, lat=40, zoom = 11) %>%
  #addProviderTiles(providers$CartoDB.DarkMatter) %>% 
  ##
  addProviderTiles(providers$CartoDB.DarkMatter, group="Dark") %>%
  addProviderTiles(providers$CartoDB.DarkMatterNoLabels, group="DarkLabel") %>%  
  addProviderTiles(providers$Esri.NatGeoWorldMap, group="Esri") %>%
  #addTiles(providers$CartoDB.PositronNoLabels) %>%
  #addControl(rr, position = "topleft", className="map-title") %>%
  ## mini reference map
  addMiniMap() %>%
  ## neighborhood boundary
  addPolygons(data = phillyNeighbor,
              color = 'skyblue',
              weight = 1)  %>%
  addCircleMarkers(lng = ~point_x,
                   lat = ~point_y,
                   label=~label.msg,
                   color=~fatalColor) %>%
# Trend of crimes over the years
addCircleMarkers(data = media, 
                 color = "red",
                 weight = 2,
                 label = "Trend",
                 stroke = FALSE, 
                 fillOpacity = 0.95,
                 group = "media") %>%
addPopupImages(trend, 
                 width = 500,
                 height = 350,
                 tooltip = FALSE,
                 group = "media") %>%
##
browsable()
```

<BR>
This map shows the shooting victims of Philadelphia from 2015 to 2024. The victims are regional clustered. The popup bar chart shows that 1) the victims are between 1250 to 2250 each year; 2) the victims significantly increase in 2020 - 2022, including fatal victims. 
<BR>